---
title: "connector.logger"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`connector.logger` is a package that provides a set of functions **to connect to data source** and read and write data from it. 

## Introduction

This vignette demonstrates how to use the `connector.logger` package to connect to 
data source and access different types of data.

First let's load all the packages we're going to use in this vignette:
```{r eval=FALSE}
library(connector.logger)
```

## Connect to data source

When we want to connect to data source we can use...

```{r eval=FALSE}  
# Load data connection
con <- ...
```

After the setup is done we can use these connection to read and write data from
data source.

## Reading and writing data

The `connector.logger` package provides a set of functions to read and write data
from the data source. 

Here is an example of reading and writing data:

```{r eval=FALSE}
# Read data
con$read_cnt()

# Write data
con$write_cnt()

```

## Conclusion

In this vignette we showed how to connect to data source, read and write
data from it.
